\section{Proposed Approach}
\label{sec:proposed-approach}

Our proposed tool consists of three components. First an
instrumentation and profiling tool which automatically adds control
flow logging statements into the source of a program. Second a tool
for generating unlikely control flow paths from the control flow path
profile. Third a symbolic execution engine which can augment network
payloads in order to force the program down the desired control flow
path.  \\
%
\noindent\textbf{Control Flow Profiling:} A control flow profile of a
program is the list of branches taken during its execution. Our goal
is to compile a profile of the control flow executed from the point
that messages are received in a distributed system. Using the AST of a
program all branching statements can be enumerated. We propose to
instrument source code by traversing a programs AST and injecting a
function to log a unique symbol at each branching statement. The
logging statements will append the unique symbols together as each
branch is executed composing a word of symbols. The end of each work
is signalled by messages being received.  \\
%
\noindent\textbf{Generating Unlikely Paths:} After a sufficient amount
of execution time the collection of words will profile typical control
flow of the system. To generate unlikely control flow paths we will
generate words which are unlike the one observed in the profile. Doing
so will be the job of a compression algorithm and an SMT solver.
Compressing the words will generate small encodings for common paths,
and long encodings for uncommon paths. We will then query the SMT
solver for a word which results in a long encoding.  \\
%
\noindent\textbf{Symbolic Execution:} Our approach requires symbolic
execution to determine which modifications to network payloads will
result in the execution of an unlikely control flow path. To begin
with we will manually construct a symbolic representation of a
distributed program. Manual symbolic execution will allow us to test
the feasibility of our approach and determine if paths can be
determined in a reasonable amount of time. We will use
Z3~\cite{4144534} as our symbolic execution engine. If our initial
approach is feasible we will extend symbolic execution by leveraging
several off the shelf solutions. To our knowledge no symbolic
execution engines exist for Go. KLEE is a symbolic execution engine
designed for C and C++~\cite{Cadar_klee:unassisted}. Our plan is to
transpile Go into C++ using the Tardis Go transpiler~\cite{tardisgo},
and execute the C++ translation with KLEE.


