\section{Proposed Approach}
\label{sec:proposed-approach}

Our proposed tool consists of three components. First an
instrumentation and profiling tool which automatically adds control
flow logging statements into the source of a program. Second a tool
for generating unlikely control flow paths from the control flow path
profile. Third a symbolic execution engine which can augment network
payloads in order to force the program down the desired control flow
path.
\\
\noindent\textbf{Control Flow Profiling:} A control flow profile of a program
is the list of branches taken during its execution. Our goal is to
compile a profile of the control flow executed from the point that
messages are received in a distributed system. Using the AST of a
program all branching statements can be enumerated. We propose to
instrument source code by traversing a programs AST and injecting a
function to log a unique symbol at each branching statement. The
logging statements will append the unique symbols together as each
branch is executed composing a word of symbols. The end of each work is
signalled by messages being received. 
\\
\noindent\textbf{Generating Unlikely Paths:} After a sufficient amount of
execution time the collection of words will profile typical control
flow of the system. To generate unlikely control flow paths we will
generate words which are unlike the one observed in the profile. Doing
so will be the job of a compression algorithm and an SMT solver.
Compressing the words will generate small encodings for common paths,
and long encodings for uncommon paths. We will then query the SMT
solver for a word which results in a long encoding.
\\
\noindent\textbf{Symbolic Execution:}
